---
title: "R Project 1 - Hello R"
author: "Dr. Katherine Shoemaker"
date: "1/23/2020"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

```datasaurus_dozen``` is dataframe with 1846 rows and 3 variables, namely, **dataset**, **x**, and **y**.

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset: 

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
```{r cor-star}
star_data %>%
  summarize(r=cor(x,y))

```
The dino data and the star data have similar r-values, -0.06447185 and -0.0629611, respectively. Take note that their are very similiar, approximately ~ 0.06. More importantly, the r-values are close to 0. With an r-value near 0, the datasets demonstrate numerically that its shape is not linear as well as graphically when we look at their plots. (And of course, a star and a dinosaur do not look like lines!)
### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}
```

```{r}
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)
